\documentclass{beamer}
\usepackage{minted}
\usetheme{Copenhagen}
\author[nemo,mastergreg]{Greg (mastergreg) Liras, John (nemo) Giannelos}
\institute{foss.ntua}
\title{Python Tutorial}
\subtitle{Part I}

\date{\today}

\begin{document}
\AtBeginSection[]
{
    \begin{frame}
        \frametitle{Outline}
        \tableofcontents[currentsection]
    \end{frame}
}
%--- the titlepage frame -------------------------%
\begin{frame}
    \titlepage
\end{frame}


\section{Introduction to Python}

\subsection{What is Python?}
\begin{frame}
    \frametitle{What is Python?}
    \begin{quote}
        Python is an easy to learn, powerful programming language. It has efficient
        high-level data structures and a simple but effective approach to
        object-oriented programming. Python’s elegant syntax and dynamic typing,
        together with its interpreted nature, make it an ideal language for scripting
        and rapid application development in many areas on most platforms.
    \end{quote}
\end{frame}

\subsection{Freatures of Python}
\begin{frame}
    \frametitle{Features (some of them)}

    In a few words, Python,
    \begin{itemize}
        \item<1-> is \emph{Scripting Language}
        \item<2-> is \emph{Strongly Typed}
        \item<3-> is \emph{Dynamic}
        \item<4-> is \emph{Interpreted}
        \item<5-> is \emph{Portable}
        \item<6-> is \emph{Object Oriented}
        \item<7-> has \emph{Vast Libraries (batteries included)}
        \item<8-> is \emph{Simple and non-obtrucive}
    \end{itemize}

\end{frame}

\subsection{Why Python?}
\begin{frame}
    \frametitle{Why?}
    \begin{itemize}
        \item<1-> It is easy to remember
        \item<2-> You can develop rapidly
        \item<3-> Readable Code (whitespace is semantically important!)
        \item<4-> Interface with C libraries
    \end{itemize}
\end{frame}
\subsection{Dos and Don'ts}

\begin{frame}[fragile]
    \frametitle{Bad Practices}

    \begin{itemize}
        \item<1-> Inventing the wheel
        \item<2-> One-liners - Obfuscated coding
        \item<3-> Having code on top level
        \item<4-> Huge imports
            \begin{minted}[fontsize=\scriptsize]{python}
>>> from foo import *
            \end{minted}
    \end{itemize}

\end{frame}

\begin{frame}[fragile]
    \frametitle{Good Practices}

    \begin{itemize}
        \item<1-> Search first code less
        \item<2-> Use env to locate your interpreter
        \item<3-> Import only what you need
        \item<4-> Run pychecker on your code
        \item<5-> 
            \begin{minted}[fontsize=\scriptsize]{python} 
if __name__ == "__main__":
    main()
            \end{minted}
    \end{itemize}

\end{frame}

\section{Python Standard Types}
\subsection{Arithmetic}

%{{{ Numeric types
\begin{frame}
    \frametitle{Numeric types}
    \begin{itemize}
        \item<1-> int ( limitless :-D )
        \item<2-> float (53 bits precision)
        \item<3-> complex ($1+2j$)
    \end{itemize}
\end{frame}
%}}}

%{{{ Operators
\begin{frame}
    \frametitle{Operators}
    \begin{itemize}
        \item<1-> + (add)
        \item<2-> - (subtract)
        \item<3-> * (multiply)
        \item<4-> / (divide)
        \item<5-> \% (modulo)
        \item<6-> =	(assign)
    \end{itemize}
\end{frame}
%}}}


%{{{ Strings
\subsection{Strings}
\begin{frame}[fragile]
    \frametitle{Strings}
    \begin{itemize}
        \item<1-> Strings are not lists! Strings are immutable!
        \item<2-> Simple concatenation: 
            \begin{minted}[fontsize=\scriptsize]{python}
>>> 'Hello' + 'World'
'HelloWorld'
            \end{minted}
        \item<3-> Slicing:
            \begin{itemize}
                \item<4->\begin{minted}[fontsize=\scriptsize]{python}
>>> 'HelloWorld'[0]
'H'
                    \end{minted}

                \item<5->\begin{minted}[fontsize=\scriptsize]{python}
>>> 'HelloWorld'[6:]
'orld'
                    \end{minted}

            \end{itemize}
        \item<6-> Unicode Strings:

            \begin{minted}[fontsize=\scriptsize]{python}
>>> ur'Hello\u0020World !'
u'Hello World !'
            \end{minted}

    \end{itemize}
\end{frame}
%}}}

\subsection{Data Structures}

%{{{ Lists
\begin{frame}[fragile]
    \frametitle{Lists}
    \begin{itemize}

        \item<1-> \begin{minted}[fontsize=\scriptsize]{python}
>>> a = ['spam', 'eggs', 100, 1234]
>>> a
['spam', 'eggs', 100, 1234]
            \end{minted}

        \item<2-> Negative indices:
            \begin{minted}[fontsize=\scriptsize]{python}
>>> a[-2]
100
            \end{minted}

        \item<3-> Concatenation:
            \begin{minted}[fontsize=\scriptsize]{python}
>>> a[:2] + ['bacon', 2*2]
['spam', 'eggs', 'bacon', 4]
            \end{minted}

        \item<4-> Comprehension:
            \begin{minted}[fontsize=\scriptsize]{python}
for i in a:
    print i
            \end{minted}

    \end{itemize}
\end{frame}
%}}}

%{{{ Tuples
\begin{frame}
    \frametitle{Tuples}
    \begin{itemize}
        \item<1-> Immutable (just as strings)
        \item<2-> Indexed
        \item<3-> Nested
    \end{itemize}
\end{frame}
%}}}

%{{{ Sets
\begin{frame}[fragile]
    \frametitle{Sets}
    \begin{quote}
        A set is an unordered collection with no duplicate elements. 
    \end{quote}
    \begin{itemize}
        \item<2-> \begin{minted}[fontsize=\scriptsize]{python}
>>> basket = ['apple', 'orange', 'apple', 'pear', 'orange', 'banana']
>>> set(basket)
set(['orange', 'pear', 'apple', 'banana'])
            \end{minted}
        \item<3-> Operators: 
            \begin{itemize}
                \item<4-> a - b (in a but not in b)
                \item<5-> a $\vert$ b (in a or in b)
                \item<6-> a \& b (in a and in b)
                \item<7-> a \textasciicircum  b (in a or b but not in both)
            \end{itemize}
    \end{itemize}
\end{frame}
%}}}

%{{{ Dictionaries
\begin{frame}[fragile]
    \frametitle{Dictionaries}
    Maps of objects
    \begin{itemize}
        \item<2-> Easy to create \begin{minted}[fontsize=\scriptsize]{python}
>>> dict([('sape', 4139), ('guido', 4127), ('jack', 4098)])
{'sape': 4139, 'jack': 4098, 'guido': 4127}
            \end{minted}
        \item<3-> Simple to use \begin{minted}[fontsize=\scriptsize]{python}
>>> tel = dict([('sape', 4139), ('guido', 4127), ('jack', 4098)])
>>> tel['jack']
4098
            \end{minted}
    \end{itemize}
\end{frame}
%}}}

\subsection{Epilogue}
\begin{frame}
    \frametitle{Questions??}
    Ask! :)
\end{frame}

\begin{frame}[fragile]
    \frametitle{Thanks}
    \begin{itemize}
        \item Thanks for watching
        \item Thanks to foss-ntua for hosting
    \end{itemize}
\end{frame}

\end{document}
